


##What am I looking for?
  I would like to know the relationship between droupout rate(county) and other social indicators. For example, how does school districts' total budget, median household income and unemployment rate affect the droupout rate? Are they positive correlation? Or are there significant difference between rural and urban areas? After all, I would like to present my findings in a map and provide some general suggestions for WA government in the executive summary.

Here are the links that my data comes from:

1.Shape File: 
https://data.wa.gov/Demographics/WAOFM-GIS-County-Boundary/sep2-mdr8/data

2.Rural and urban areas: https://www.doh.wa.gov/Portals/1/Documents/1500/RUCAGuide.pdf

3.Census Data:
State of Washington Open Data Platform and 
http://data.spokesman.com/census/2010/washington/counties/

4.School Districts and Public Schools' data:
National Center for Education Statistics
https://www.ofm.wa.gov/washington-data-research/population-demographics/population-estimates/small-area-estimates-program

5.Schools' budgets:
https://nces.ed.gov/edfin/search/peergroupdata.asp?dataid=1&subdataid=1&mt=0&jobid={CDB9F6CF-266C-41A9-87ED-E0867B2EA370}

6.Household Incomes:
https://www.ofm.wa.gov/sites/default/files/public/legacy/economy/hhinc/medinc.pdf

7.Droupout rates:
https://dev.socrata.com/foundry/data.wa.gov/6g87-pu72



##Part1. Reading the data 

```{r}
dropout<-read.csv("https://github.com/liuuw/PROJECT/raw/master/Dataset.csv")

dim(dropout)
names(dropout)
```

I choose some of relevent variables in the dataset that I think might have connection with the dependent varibable(dropout rates) to do the analysis.

Since there's no missing value in WA counties' census records or schools' data, basic excel function like 'if','countif','sum' can clean the data well. 

We can see that there are 39 counties in WA. I pick up 14 possible independent variables in total for each county and am wandering which might relate to the droupout rate best. After try and error, this analysis will focus more on 'total revenue per student,''median household income,' and 'unemployment rate.'

There are also 39 counties in the attribute table of the WA shape file, which is really handy for us to merge the data and show it on the map. 

For now, let's look at the univariate exploration first. 

```{r}
str(dropout)
```
##Univariate exploration:
Turn our attention to counties whose been classified as Rural/Urban. This is the distribution of its values nad its relative frequencies.
```{r}
is.data.frame(dropout)
length(dropout)
table(dropout$Region)
prop.table(table(dropout$Region))
```

Then we can run Chi-square test to see if the difference is significant and how's the measure of centrality for the Region (dichotomous values):
```{r}
library(tidyverse)
prop.table(table(dropout$Region))%>%chisq.test() # In order to see the value of X-squared

distribution= table(dropout$Region) # To see whether Rural or Urban area are the counities in
modeCount=max(distribution)
mode=distribution[distribution==modeCount]
names(mode)
```


##Part.II Take a look at the data
Let's see the school districts' revenue difference among these 39 counties and sort by their budget. (ggplot)
```{r}
library(ggthemes)
library(tidyverse)
library(ggplot2)

dropout %>% 
  group_by(County) %>% 
  summarise(avg_amount = mean(TotalRevenuePerStudent, na.rm = TRUE)) %>%
  ggplot(aes(reorder(County, -avg_amount), avg_amount)) +
  geom_bar(stat = 'identity') + 
  scale_y_continuous() + theme_classic() + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))


```

Let’s consider for this section the variable that tells us the highest total dropout rate and revenue according to each county.

```{r}
library(DescTools)
max(dropout$TotalRevenuePerStudent)
min(dropout$TotalRevenuePerStudent)
Median(dropout$TotalRevenuePerStudent)

max(dropout$Dropout_Rate)
min(dropout$Dropout_Rate)
Median(dropout$Dropout_Rate)

```

##Skewness and Kurtosis

We don't need to do skewness and kutosis for this dataset, this part can be seemed as a practice.
```{r}
library(moments)
skewness(dropout[,c(2:16)],na.rm = T) 
```

```{r}
library(moments)
kurtosis(dropout[,c(2:16)],na.rm = T)

```

```{r}
# getting the 'years'
county=names(kurtosis(dropout[,c(2:16)],na.rm = T))


library(stringr)
library(moments)
county =str_extract(county, "\\d+")

# now we continue:
kt=kurtosis(dropout[,c(2:16)],na.rm = T)
sk=skewness(dropout[,c(2:16)],na.rm = T) 
par(mfrow=c(2,1))
plot(sk,type = 'l',col='blue',ylab='skewness')
plot(kt,type = 'l',col='red',ylab='kurtosis')
```




##Histogram
From the previous part(max, min, median), we can see that the differences among counties are big, so we might want to understand their distributions a bit deeper.

```{r}
par(mfrow = c(2,2)) 
hist(x=dropout$Dropout_Rate, 
     main="Histogram of Dropout Rate",         # Name of picture
     xlab="Numbers of County (39 Counties in Total)",                      # Name of X-axis
     ylab="Number of counties") 
hist(dropout$unemployment_rate,
     main="Histogram of Unemployment Rate",         # Name of picture
     xlab="Unemployment Rate 2012",                      # Name of X-axis
     ylab="Number of counties")
hist(x=dropout$TotalRevenuePerStudent, 
     main="Histogram of Total Revenue",         # Name of picture
     xlab="Revenue($)",                      # Name of X-axis
     ylab="Number of counties") 

hist(x=dropout$Median_household_income_2012, 
     main="Histogram of Household Income",         # Name of picture
     xlab="Income($)",                      # Name of X-axis
     ylab="Number of counties ")
```

##Boxplot
```{r}
par(mfrow = c(1,3)) 
boxplot(dropout$Median_household_income_2012,	xlab="Household Income 2012", ylab="Dollars")
boxplot(dropout$unemployment_rate,	xlab="Unemploymet Rate 2012", ylab="Percent")
boxplot(dropout$TotalRevenuePerStudent,	xlab="Total Revenue Per Student", ylab="Dollars")
```
```{r}
par(mfrow = c(1,2)) 
boxplot(dropout$single_female_with_children,	xlab="Single Mother Rate 2012", ylab="Percent")
boxplot(dropout$Dropout_Rate,	xlab="Dropout Rate 2012", ylab="Percent")
```

##Regression
Here shows the correlation coefficient between each variables and whether it is signicicative.
We can see that all the variables do Not reaching a statistically significant level, which means my data can't properly catch the social complexity. If we have more theoretical support for choosing independent, we may improve this situation.
Also, some of the correlation coefficients within my independent variables are too high,like "TotalRevenuePerStudent," "TotalFederalRevenuePerStudent," "TotalLocalRevenuePerStudent" and    "TotalStateRevenuePerStudent," which may affect the accuracy of the analysis. 
```{r}
explanans=names(dropout)[c(3,4,5,7,8,9,10,11,12,13,14,15,16)]
for (x in explanans){
    par=cbind(dropout[,x],dropout$Dropout_Rate)
    p=cor.test(dropout[,x],dropout$Dropout_Rate)
    print(paste("Pearson:",p$estimate," - Is significative?",p$p.value<0.05))
}


cor(dropout[explanans])
```


#### Here shows the plot of the highest correlation coefficient of my chosen variables and the dropout rate.

Pearson =0.306
```{r}

plot(x=dropout$Dropout_Rate,      #  Values for X axis
     y=dropout$unemployment_rate,       # Values for Y axis
     main="Correlation Between Unemployment Rate and Dropout Rate",    # Title
     xlab="Dropout Rate(%)",       # Name of X axis
     ylab="Unemploymeny rate(%)"         # Name of Y axis
)

abline(lm(unemployment_rate~ Dropout_Rate, data=dropout))  # Linear model


```


Pearson=0.08
```{r}
plot(x=dropout$Dropout_Rate,      #  Values for X axis
     y=dropout$single_female_with_children,       # Values for Y axis
     main="Correlation Between Dropout Rate and the Ratio of Single Mother",    # Title
     xlab="Dropout Rate(%)",       # Name of X axis
     ylab="The Proportion of Single Mother (%)"         # Name of Y axis
)
abline(lm(single_female_with_children~ Dropout_Rate, data=dropout))
```

#Mutiple Regression
We told R that the Y (dropout rate) is to be regressed (~) by all those X variables ( TotalFederalRevenuePerStudent + unemployment_rate + single_male_with_children)

From the results, we can see that the p-value is 0.4797>0.05 and the R-squared is 0.09491,  so our indenpendent variables can only limitedly explain the denpendent varibale.
```{r}
row.names(dropout)=dropout$County

LinRegEPI = lm(Dropout_Rate ~ TotalFederalRevenuePerStudent + unemployment_rate + single_male_with_children + Median_household_income_2012, 
               data = dropout)

summary(LinRegEPI)
```
The adjusted R-squared usually is  from 0 to 1, the closer to 1 the better, and ours is -0.01, which means a little.

```{r}
results=coef(summary(LinRegEPI))

data.frame(Coefficient=results[,1],Significant=results[,4]<0.05)

summary(LinRegEPI)$adj.r.squared 
```

##Logistic Regression

We run logistic regression and find out that the binomianl variable (Region: Urban/ country) don't  affect those variables and don't reach a siginificant level statistically. So, my data shows that there are no significant difference between rural and urban areas.
```{r}

LogitEPI_a = glm(factor(Region) ~ TotalFederalRevenuePerStudent + unemployment_rate + Dropout_Rate, 
                  data = dropout, family = binomial()
                  )

results=coef(summary(LogitEPI_a))
data.frame(CoefficientExp=exp(results[,1]),Significant=results[,4]<0.05)
```
##Clustering
From the dendrogram, we can see that King county is the outliner of the data, I use different methods(average and ercliedean) to classify my data, both show the similar reseult. 

NOTE: The following two plots are ploted according to all the independent variables.
```{r}
library(cluster)
row.names(dropout)=dropout$County
demoSimi=daisy(dropout[,c(2:16)],metric = "euclidean",
               stand=TRUE)
demoClus=hclust(demoSimi,method = 'average')
plot(demoClus,cex=0.5)


```


```{r}
data <- dropout[, -1]
E.dist <- dist(data, method="euclidean")
E.dist %>% hclust()%>% plot()%>% par(mfrow=c(1,2))
library("tidyverse")
Cluster<-data%>% dist(method="euclidean")%>% hclust(method= "ward.D2")

```


##Mapping 
```{r}
library(jsonlite)
is.data.frame(dropout)  
dropout1=dropout[,c('County','TotalRevenuePerStudent','Student_number')]
str(dropout1)
Map="https://github.com/liuuw/PROJECT/raw/master/WAOFM%20-%20GIS%20-%20County%20Boundary.zip"
```
We load the Shape file first.

```{r}
library(utils)
temp=tempfile()
download.file(Map, temp)
unzip(temp)
(maps=list.files(pattern = 'shp'))

library(rgdal)
wazipMap <- rgdal::readOGR("geo_export_109cf655-8ce8-4eea-8b93-dc816b22de53.shp",stringsAsFactors=F) # use name
names(wazipMap)
str(wazipMap$name)
str(dropout$County)
contribWAmap=merge(wazipMap,dropout, by.x='name', by.y='County',all.x=F)
nrow(contribWAmap)
plot(wazipMap,col='black')
plot(contribWAmap,col='pink',border='grey',add=T)
```


And plot it with different colors in terms of the Dropout rate, Number of students, Number of Schools and Total Revenue.

###Map.1
```{r}
library(RColorBrewer)
library(classInt)
varToPLot=contribWAmap$Dropout_Rate

numberOfClasses = 5
colorForScale='YlGnBu'
colors = brewer.pal(numberOfClasses, colorForScale)
intervals <- classIntervals(varToPLot, numberOfClasses, 
                            style = "quantile",
                            dataPrecision=2)
colorPallette <- findColours(intervals, colors)

legendText="Dropout rate (%)"
shrinkLegend=0.4
title="Dropout Rate by County"

plot(wazipMap,col='red',main=title)
plot(contribWAmap, col = colorPallette,border='grey',add=T)

legend('topright', legend = names(attr(colorPallette, "table")), 
       fill = attr(colorPallette, "palette"), cex = shrinkLegend, 
       bty = "n",
       title=legendText)
```

###Map.2
```{r}
library(RColorBrewer)
library(classInt)
varToPLot=contribWAmap$Student_number

numberOfClasses = 5
colorForScale='YlGnBu'
colors = brewer.pal(numberOfClasses, colorForScale)
intervals <- classIntervals(varToPLot, numberOfClasses, 
                            style = "quantile",
                            dataPrecision=2)
colorPallette <- findColours(intervals, colors)

legendText="Number of students(%)"
shrinkLegend=0.4
title="Number of Students "

plot(wazipMap,col='red',main=title)
plot(contribWAmap, col = colorPallette,border='grey',add=T)

legend('topright', legend = names(attr(colorPallette, "table")), 
       fill = attr(colorPallette, "palette"), cex = shrinkLegend, 
       bty = "n",
       title=legendText)
```
###Map.3
```{r}
library(RColorBrewer)
library(classInt)
varToPLot=contribWAmap$Number_of_public_schools

numberOfClasses = 5
colorForScale='YlGnBu'
colors = brewer.pal(numberOfClasses, colorForScale)
intervals <- classIntervals(varToPLot, numberOfClasses, 
                            style = "quantile",
                            dataPrecision=2)
colorPallette <- findColours(intervals, colors)

legendText="Number of Schools"
shrinkLegend=0.4
title="Number of Public Schools for Each County"

plot(wazipMap,col='red',main=title)
plot(contribWAmap, col = colorPallette,border='grey',add=T)

legend('topright', legend = names(attr(colorPallette, "table")), 
       fill = attr(colorPallette, "palette"), cex = shrinkLegend, 
       bty = "n",
       title=legendText)
```


###Map.4
```{r}
library(RColorBrewer)
library(classInt)
varToPLot=contribWAmap$TotalRevenuePerStudent

numberOfClasses = 5
colorForScale='YlGnBu'
colors = brewer.pal(numberOfClasses, colorForScale)
intervals <- classIntervals(varToPLot, numberOfClasses, 
                            style = "quantile",
                            dataPrecision=2)
colorPallette <- findColours(intervals, colors)

legendText="Revenue Per student($)"
shrinkLegend=0.4
title="Total Revenue Per Student In WA"

plot(wazipMap,col='red',main=title)
plot(contribWAmap, col = colorPallette,border='grey',add=T)

legend('topright', legend = names(attr(colorPallette, "table")), 
       fill = attr(colorPallette, "palette"), cex = shrinkLegend, 
       bty = "n",
       title=legendText)
```







